---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.retina = 2,
  fig.path = "README-"
)
```

    __________________________oooo__oo____________________
    _ooooo__oo_ooo___ooooo___oo_____oo_____ooooo__oo_ooo__
    oo___oo_ooo___o_oo___oo_ooooo__oooo___oo____o_ooo___o_
    oo______oo______oo___oo_oo______oo____ooooooo_oo______
    oo______oo______oo___oo_oo______oo__o_oo______oo______
    _ooooo__oo_______oooo_o_oo_______ooo___ooooo__oo______
    ______________________________________________________
    
crafter is eventually going to be a R pacakge to work with PCAP dumps

Life's too short to export to CSV/XML. There's no reason R should not be able to read binary PCAP data.

[What is a PCAP?](https://en.wikipedia.org/wiki/Pcap)

You need the [crafter C++ library](https://github.com/pellegre/libcrafter), which lists the other dependencies.

If there's any hope for this to run on Windows (`libcrafter` supports Windows) it will be due to a Windows + (prbly some infosec) + `#rstats` person tagging along on this project.

The following functions are implemented:

- `read_pcap`: for now, it pulls IP packet metadata from PCAP dumps. The whole works is planned, tho.

### News

- Version 0.0.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/crafter")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(crafter)

# current verison
packageVersion("crafter")

```

### Test Results

```{r}
library(crafter)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
